%-------------------------
% Resume in Latex
% Author : Levi Huang
% Based on: Wilmer Gonzalez template (originally Sourabh Bajaj repo)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{tcolorbox}

% Page coloring, fonts, and logos
\usepackage{pagecolor}
\usepackage{lato}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{fontawesome}
% ---

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% ---

% Sections formatting
\titleformat{\section}{
  \vspace{1pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% ---

% Custom commands

\newcommand{\sepsection}{\vspace{25pt}}

\newcommand{\resumeItem}[1]{%2
  \item\small{
    %\textbf{#1}
    #1
    %{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{8pt}\item%-1
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \vspace{1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeTech}[2]{
 \underline{#1:} #2
}

% COLOR THEMES SELECTION

% For Light theme un-comment this and comment the Dark theme section below
\tcbset{
  colback=gray!17!white,
  colframe=gray!17!white
}
\definecolor{pageLinkTextColor}{HTML}{57a2ff}
\definecolor{pageTextColor}{HTML}{262626}
\colorlet{textcolor}{pageTextColor}
\colorlet{urlcolor}{pageLinkTextColor}
\newcommand{\otherThemeRef}{\href{https://github.com/CreateWithLevi/resume/raw/master/Levi-Huang-Resume-Dark.pdf}{ Dark \color{urlcolor}{\faicon{lightbulb-o}}}}
\newcommand{\latestVersion}{\href{https://github.com/CreateWithLevi/resume/raw/master/Levi-Huang-Resume-Light.pdf}{Latest \color{urlcolor}{\faicon{refresh}}}}

\begin{document}
% ---

% For Dark theme un-comment this and comment the Light theme section above
% \tcbset{
%   colback=black!50!gray,
%   colframe=black!50!gray,
%   coltext=white!80!gray
% }
% \definecolor{pageBackgroundColor}{HTML}{171717}
% \definecolor{pageTextColor}{HTML}{d4d4d4}%d4d4d4
% \definecolor{pageLinkTextColor}{HTML}{57a2ff}
% % \colorlet{textcolor}{white!80!gray}
% \colorlet{textcolor}{pageTextColor}
% % \colorlet{backgroundcolor}{black!30!gray}
% \colorlet{backgroundcolor}{pageBackgroundColor}
% \colorlet{urlcolor}{pageLinkTextColor}
% \AtBeginDocument{\color{textcolor}}
% \newcommand{\otherThemeRef}{\href{https://github.com/CreateWithLevi/resume/raw/master/Levi-Huang-Resume-Light.pdf}{Light \color{urlcolor}{\faicon{lightbulb-o}}}}
% \newcommand{\latestVersion}{\href{https://github.com/CreateWithLevi/resume/raw/master/Levi-Huang-Resume-Dark.pdf}{Latest \color{urlcolor}{\faicon{refresh}}}}

% \begin{document}
% \pagecolor{backgroundcolor}
% ---

% HEADING
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Levi Huang} \href{https://jlstudio.xyz/Levi}{\color{urlcolor} \faicon{link}}\\
Senior Product Engineer & \href{mailto:create.with.levi@gmail.com}{\color{urlcolor}{\faicon{envelope}} \color{textcolor} create.with.levi} \\
  \textsl{Berlin, Germany} & \href{https://linkedin.com/in/li-wei-huang}{ \color{urlcolor}{\faicon{linkedin}} \color{textcolor} li-wei-huang} \\
  \textsl{+49 151 29542557} & \href{https://github.com/CreateWithLevi}{  \color{urlcolor}{\faicon{github}} \color{textcolor} CreateWithLevi}\\
  % \href{maybe}{\color{urlcolor}{\faicon{film}} \underline{\textsl{video introduction}}}
\end{tabular*}
% ---

% SUMMARY
\section{Summary}
A Product-focused Senior Engineer with 8+ years of full-stack experience building scalable web applications from concept to launch. Experienced in 0-to-1 product delivery with end-to-end ownership, from system architecture to user-facing features. Proven ability to integrate AI/LLM to improve product outcomes—reducing trading strategy creation from days to minutes. Delivered solutions across fintech, e-commerce, and enterprise SaaS.

% EXPERIENCE
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {JL Studio}{Remote}
      {Founding Engineer}{January 2021 - Present}
      
      \vspace{5pt}
      \textbf{Key Projects:}
      \resumeItemListStart
      \resumeItem{\textbf{Forexify AI Lab (AI-Powered Trading Platform):} Architected and implemented an AI-powered trading platform that reduced trading strategy creation time from days to minutes through innovative template-grounded AI code generation}
      \resumeItem{\textbf{Zuoluh (AI-Driven Fintech Platform):} Led technical architecture and prototype development for a values-driven financial platform, designing a custom RAG system architecture for financial and ESG data analysis using ChromaDB to ensure reliable and traceable insights}
      \resumeItem{\textbf{"We Are Enough" (Interactive Web Platform):} Transformed intricate Figma designs into production-ready web animations using Vue.js + GSAP, developing dynamic SVG path generation and complex scroll-driven animations}
      \resumeItem{\textbf{Apparel X (Enterprise SaaS ERP Platform):} Maintained and evolved the platform for 5+ years, modernizing the full stack (PHP, MySQL, GCP) and implementing multi-tenant architecture—demonstrating sustained client trust and system ownership}
      \resumeItem{\textbf{Temple Lighting Platform (E-commerce):} Engineered a platform that contributed to 40\% business growth through customized booking workflow design and robust performance optimization}
      \resumeItemListEnd
      \resumeTech{Company summary}{Co-founded with a designer to deliver end-to-end product development for international clients. Specialized in AI-integrated applications and scalable web solutions across fintech, e-commerce, and SaaS.}
      \begin{tcolorbox}
          \textbf{Tech:} React, Next.js, Vue.js, TypeScript, Python, PostgreSQL, GCP, AI Integration, RAG Systems, GSAP.
      \end{tcolorbox}

    \resumeSubheading
      {Stone River Information Technology}{Taipei, Taiwan}
      {Software Engineer}{December 2017 - December 2020}
      \resumeItemListStart
      \resumeItem{Engineered a cloud-based ERP system (Apparel X) to replace a legacy DOS application, collaborating with the original developer to migrate complex business logic while modernizing the architecture}
      \resumeItem{Developed enterprise business intelligence solutions for corporate clients like Asia Cement Corporation}
      \resumeItem{Implemented robust data security measures and audit trails for complex data processing requirements}
      \resumeItemListEnd
      \resumeTech{Company summary}{An IT consultancy developing enterprise business intelligence and custom management systems for corporate clients.}
      \begin{tcolorbox}
          \textbf{Tech:} Business Intelligence, Power BI, SSDT, Data Security, PHP, JavaScript, MySQL.
      \end{tcolorbox}
    
    \resumeSubheading
      {Sense Innovation}{Taipei, Taiwan}
      {Software Engineer}{May 2016 - July 2017}
      \resumeItemListStart
      \resumeItem{Developed eye-tracking assistive technology that enabled over 100 individuals with disabilities to access computing and digital communication}
      \resumeItem{Developed user-centric marketing websites to communicate complex technical product value}
      \resumeItemListEnd
      \resumeTech{Company summary}{A technology firm focused on developing eye-tracking assistive software to improve digital accessibility for individuals with disabilities.}
      \begin{tcolorbox}
          \textbf{Tech:} Eye-tracking Technology, Assistive Software, Computer Vision, C\#, HTML, CSS.
      \end{tcolorbox}

    \resumeSubHeadingListEnd

% PERSONAL PROJECTS
\section{Personal Projects \color{urlcolor}{(with links)}}
  \resumeSubHeadingListStart
    \resumeSubItem{\textbf{Microservices Trading Platform (R\&D):} Building event-driven architecture with RabbitMQ, gRPC, and Redis for high-throughput trading systems. CI/CD with Docker Compose and automated testing.}

    \resumeSubItem{\textbf{\href{https://cyclegrowth.jlstudio.xyz/}{CycleGrowth (AI-Powered SaaS)}:} Complete SaaS platform (React, Next.js, TypeScript) with AI integration, auth, and Stripe payments. Comprehensive testing coverage for stability.}

    \resumeSubItem{\textbf{\href{https://persona-muse.jlstudio.xyz/}{Persona Muse (Hackathon)}:} AI Persona Generator integrating LLMs for rapid user persona creation, demonstrating quick prototyping skills.}

  \resumeSubHeadingListEnd

% TECHNICAL SKILLS
\section{Skills}
  \resumeSubHeadingListStart

  \resumeSubItem{\textbf{Programming Languages \& Frameworks:} TypeScript, React, Next.js, Vue.js, Python (Flask), Node.js, PHP}

  \resumeSubItem{\textbf{AI/ML Integration:} LLM Integration, RAG Architecture, Prompt Engineering, AI Workflow Optimization}

  \resumeSubItem{\textbf{Cloud \& Infrastructure:} GCP, Docker, Supabase, Vercel, PostgreSQL, MySQL, MongoDB}

  \resumeSubItem{\textbf{Engineering Practices:} Agile Development, Automated Testing, CI/CD, Performance Optimization, End-to-end Development}

  \resumeSubItem{\textbf{Product \& Design:} Figma, UI/UX Design, Responsive Design, Web Animations (GSAP), Figma-to-Code}

  \resumeSubHeadingListEnd

% EDUCATION
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Chengchi University}{Taipei, Taiwan}
      {Bachelor of Science, Management Information Systems}{Sept. 2013 -- Jun. 2017}
  \resumeSubHeadingListEnd

% LANGUAGES
\section{Languages}
  \resumeSubHeadingListStart
    \resumeSubItem{\textbf{English} — Fluent}
    \resumeSubItem{\textbf{Chinese (Mandarin)} — Native}
  \resumeSubHeadingListEnd
% ---
\vspace{1em}
% \hfill \textsl{ Click on items for details. \color{urlcolor}{\faicon{link}}}



% ---
\end{document}

